Would NEMO benefit from using the \psyclone\ system?

### 2017-01-10 docs/NEMO/psyclone_and_nemo.tex
Add section on key NEMO issues that PSyclone can help with.

>>>>

\section{NEMO Performance/Maintenance Issues that \psyclone\ Could Help With}

This section contains a list of those issues that have been
highlighted at various NEMO HPC and HPC subgroup meetings that
\psyclone\ and the PSyKAl separation of concerns will help to address:

\item Removal of unecessary halo swaps - PSyclone only generates calls to
  perform halo swaps when they are necessary for correctness.

\item Ability to experiment with collecting of multiple halo swaps

\item Aiding loop vectorisation through compiler directives

\item Cache-blocking of loops to better utilise memory bandwidth

\item Support for OpenACC so that NEMO can run on GPU-based systems

\item Support for OpenMP so that NEMO can run in hybrid OpenMP/MPI mode

For invasive and repetitive code changes (such as re-structuring loops
for cache blocking) the PSyclone approach is particularly
valuable. This is because such changes are then implemented as a
PSyclone transformation which only affects the generated code - the
oceanographer does not have to worry about the resulting code
complexity (potentially a nested loop with depth six). Tuning of the
cache blocking itself can also be easily done by an HPC expert since
the PSyclone tool would apply any changes to the whole code base.
